Efficient static analysis of Marlowe contracts

### 2020-05-18 papers/static_analysis2020/paper.tex
Add template table for measurement section

\documentclass[english,runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{graphicx}
\usepackage{babel}
\begin{document}
\title{Efficient static analysis of Marlowe contracts}

@@

\paragraph*{Lightweight }

@@

@@

\section{Future work }

>>>>

\documentclass[english,runningheads]{llncs}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{graphicx}
\usepackage{babel}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}

\DeclareUnicodeCharacter{00D7}{$\times$}

\begin{document}
\title{Efficient static analysis of Marlowe contracts}

@@

\paragraph*{Lightweight}

@@

\section{Measurements}

\begin{table}[]
\begin{tabular}{l||lllll}
\multicolumn{1}{c||}{\textbf{Auction}} & \multicolumn{5}{c}{\textbf{Lightweight optimisations}} \\ \hline \hline
\textbf{Number of participants}        & \multicolumn{1}{c||}{1}        & \multicolumn{1}{c|}{2}            & \multicolumn{1}{c|}{3}                         & \multicolumn{1}{c|}{4}                        & \multicolumn{1}{c}{5}    \\ \hline
\textbf{Execution time}                & \multicolumn{1}{c||}{0.2205s}  & \multicolumn{1}{c|}{4m 45.2015s}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A} & \color[HTML]{888888} N/A \\ \hline
Generation overhead                    & \multicolumn{1}{c||}{76.61\%}  & \multicolumn{1}{c|}{96.40\%}      & \multicolumn{1}{c|}{\color[HTML]{888888} N/A}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A} & \color[HTML]{888888} N/A \\ \hline
\multicolumn{1}{r||}{× execution time} & \multicolumn{1}{c||}{0.1689s}  & \multicolumn{1}{c|}{4m 34.9342s}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A} & \color[HTML]{888888} N/A \\ \hline
Z3 overhead                            & \multicolumn{1}{c||}{23.39\%}  & \multicolumn{1}{c|}{3.60\%}       & \multicolumn{1}{c|}{\color[HTML]{888888} N/A}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A} & \color[HTML]{888888} N/A \\ \hline
\multicolumn{1}{r||}{× execution time} & \multicolumn{1}{c||}{0.0516s}  & \multicolumn{1}{c|}{10.2673s}     & \multicolumn{1}{c|}{\color[HTML]{888888} N/A}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A} & \color[HTML]{888888} N/A \\ \hline
\textbf{RAM usage peak}                & \multicolumn{1}{c||}{44,248KB} & \multicolumn{1}{c|}{1,885,928KB}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A}  & \multicolumn{1}{c|}{\color[HTML]{888888} N/A} & \color[HTML]{888888} N/A \\ \hline
\end{tabular}
\end{table}

\begin{table}[]
\begin{tabular}{l||lllll}
\multicolumn{1}{c||}{\textbf{Auction}} & \multicolumn{5}{c}{\textbf{Heavyweight optimisations}} \\ \hline \hline
\textbf{Number of participants}        & \multicolumn{1}{c||}{1}        & \multicolumn{1}{c|}{2}        & \multicolumn{1}{c|}{3}        & \multicolumn{1}{c|}{4}              & \multicolumn{1}{c}{5}    \\ \hline
\textbf{Execution time}                & \multicolumn{1}{c||}{0.01198s} & \multicolumn{1}{c|}{0.0289s}  & \multicolumn{1}{c|}{1.1138s}  & \multicolumn{1}{c|}{1h 5m 45.1377s} & \color[HTML]{888888} N/A \\ \hline
Generation overhead                    & \multicolumn{1}{c||}{83.73\%}  & \multicolumn{1}{c|}{70.36\%}  & \multicolumn{1}{c|}{75.91\%}  & \multicolumn{1}{c|}{80.86\%}        & \color[HTML]{888888} N/A \\ \hline
\multicolumn{1}{r||}{× execution time} & \multicolumn{1}{c||}{0.0100s}  & \multicolumn{1}{c|}{0.0203s}  & \multicolumn{1}{c|}{0.8455s}  & \multicolumn{1}{c|}{53m 10.0383s}   & \color[HTML]{888888} N/A \\ \hline
Z3 overhead                            & \multicolumn{1}{c||}{16.27\%}  & \multicolumn{1}{c|}{29.64\%}  & \multicolumn{1}{c|}{24.09\%}  & \multicolumn{1}{c|}{19.14\%}        & \color[HTML]{888888} N/A \\ \hline
\multicolumn{1}{r||}{× execution time} & \multicolumn{1}{c||}{0.0019s}  & \multicolumn{1}{c|}{0.0086s}  & \multicolumn{1}{c|}{0.2683s}  & \multicolumn{1}{c|}{12m 35.0993s}   & \color[HTML]{888888} N/A \\ \hline
\textbf{RAM usage peak}                & \multicolumn{1}{c||}{17,020KB} & \multicolumn{1}{c|}{17,740KB} & \multicolumn{1}{c|}{49,668KB} & \multicolumn{1}{c|}{2,364,500KB}    & \color[HTML]{888888} N/A
\end{tabular}
\end{table}

@@

\section{Future work}
